Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-10-24 manuscript.tex
overleaf update

However, these detectors exhibit photon number number dependent responses that affect the time-correlated measurements needed for high-rate PPM. This behavior, shown in Fig.~\ref{fig:waveform} is also known as photon number resolution (PNR) -- a property that is desirable in certain applications including quantum communication and quantum computing. The SNSPD generates RF pulses with greater amplitude and slew rate when detecting optical pulses with multiple photons. Photon number effects are especially evident in this lower jitter variety of SNSPD due to the use of impedance matching tapers which more efficiently couple energy out of the nanowire and into the readout circuit. With high resolution time tagging equipment, photon number dependent effects have even been observed in SNSPDs not necessarily designed to exhibit it \citep[\cite{sauer2023resolving}]{schapeler2023superconducting} like those without tapers \cite{Cahall2017SlewRatePNR}. Therefore it is increasingly likely that future research involving low-jitter SNSPDs and multiphoton pulsed sources will have to explicitly manage the PNR response for accurate time-correlated measurements -- whether the effect it is desired or not.

>>>>

However, these detectors exhibit photon number number dependent responses that affect the time-correlated measurements needed for high-rate PPM. This behavior, shown in Fig.~\ref{fig:waveform} is also known as photon number resolution (PNR) -- a property that is desirable in certain applications including quantum communication and quantum computing. The SNSPD generates RF pulses with greater amplitude and slew rate when detecting optical pulses with multiple photons. Photon number effects are especially evident in this lower jitter variety of SNSPD due to the use of impedance matching tapers which more efficiently couple energy out of the nanowire and into the readout circuit. With high resolution time tagging equipment, photon number dependent effects have even been observed in SNSPDs not necessarily designed to exhibit it \cite{schapeler2023superconducting, sauer2023resolving} like those without tapers \cite{Cahall2017SlewRatePNR}. Therefore it is increasingly likely that future research involving low-jitter SNSPDs and multiphoton pulsed sources will have to explicitly manage the PNR response for accurate time-correlated measurements -- whether the effect it is desired or not.
